---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# leaflethex

<!-- badges: start -->
<!-- badges: end -->

The goal of leaflethex is to create hexbin layers that can be added to plots made
with the leaflet package. 

This is a work in progress and is not yet a functional R package.  Stay tuned!

## Installation

You can install the released version of leaflethex from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("leaflethex")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("rpruim/leaflethex")
```
## Example

This is a basic example which shows you how to add the hexbin layer to your leaflet map:

```{r example, eval = FALSE}
library(leaflethex)
df = tibble(
  lat = rnorm(100),
  lng = rnorm(100)
)
map <- leaflet::leaflet(df) %>% 
  leaflet::addTiles() %>% 
  leaflethex::addHexbin(
    radius = 19, 
    lowEndColor = "yellow", 
    highEndColor="red")
map
```

## Parameters for addHexbin

* `data` - data frame or tibble - alternate data to use for this hexbin instead of default map data
* `radius` - numeric - choose the base size for the hexagons
* `opacity` - decimal - between 0.0 and 1.0 - choose the percent of opacity for the hexagons
* `duration` - numeric - positive milliseconds taken by the renderer to draw the hexagons
* `lowEndColor` - string - choose the color for the smaller hexagons
* `highEndColor` - string - choose the color for the larger hexagons

    _Note About Coloring_ - For best readable results, use colors that have high contrast in hue and shade such as red and yellow. White is generally a safe option for the `lowEndColor`, but the eye is better at picking up changes in hue than changes in shade. Blue to Yellow is also a good option. Generally `highEndColor` and `lowEndColor` should be opposites in terms of brightness.
    
* `uniformSize` - boolean - choose if the size of the hexagons should be uniform or variable
* `uniformColor` - string - choose a color to be uniform across the different sizes of hexagons instead of variable color
* `sizeSummaryFunction` - string - choose a function from 'count', 'sum', 'max', 'min', 'mean', or 'median' or give a valid JS function (in development)
* `sizevar` - string - the name of the variable used to calculate the size of the hex using the `sizeSummaryFunction`
* `colorSummaryFunction` - string - choose a function from 'count', 'sum', 'max', 'min', 'mean', or 'median' or give a valid JS function (in development)
* `colorvar` - string - the name of the variable used to calculate the color of the hex using the `colorSummaryFunction`
