---
title: "Hexbin Layer Demo"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Learning-leaflet}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, include = FALSE}
library(htmlwidgets)
library(htmltools)
library(dplyr)
library(leaflethex)
library(leaflet)
```

```{r}
df <- tibble(
  lat = rnorm(100),
  lng = rnorm(100)
)

df2 <- tibble(
  lat =  42.9634 + rnorm(1000),
  lng = -85.6681 + rnorm(1000)
)

df3 <- tibble(
  lat =  51.8126 + rnorm(1000),
  lng = 5.8372 + rnorm(1000)
)

df4 <- tibble(
  lat =  30.2460 + rnorm(1000),
  lng = -87.7008 + rnorm(1000)
)
```


```{r}
leaflet::leaflet(df, width = 600, height = 300) %>% 
  addTiles() %>% 
  addHexbin(
    radius = 19, 
    lowEndColor = "yellow", 
    highEndColor="red") %>%
  addHexbin(
    data = df2,
    radius = 16, 
    lowEndColor = "lightblue", 
    highEndColor="purple") %>%
  addHexbin(
    data = df3,
    uniformSize = TRUE,
    lowEndColor = 'yellow',
    highEndColor = 'red') %>%
  addHexbin(
    data = df4,
    uniformColor = 'green',
    radius = 18)
```


## Calculating the Hexbin with data other than the latitude and longitude

By default, `addHexbin()` uses hexagans to represent counts -- the number of
latitude/longitude pairs in each hexagonal bin. It is also possible to represent
the value of a summary function applied to some variable in the data. Summary
functions currently supported are min, max, mean, and median. To use a summary
function, simply supply the summary function and the name of the variable containing
the data to summarize.

```{r}
kids_df <- tibble(
  lat =  33.2460 + rnorm(1000),
  lng = -89.7008 + rnorm(1000),
  sample_size = sample(x = 1:5, size = 1000, replace = TRUE)
)
temp_df <- tibble(
  lat =  42.2460 + rnorm(1000),
  lng = -87.7008 + rnorm(1000),
  temp = sample(x = 20:100, size = 1000, replace = TRUE)
)
both_df <- tibble(
   lat =  40.0150 + rnorm(1000),
  lng = -105.2705 + rnorm(1000),
  sample_size = sample(x = 1:5, size = 1000, replace = TRUE),
  temp = sample(x = 20:100, size = 1000, replace = TRUE)
)
leaflet::leaflet(kids_df, width = 600, height = 300) %>% 
  addTiles() %>% 
  addHexbin(
    radius = 19, 
    lowEndColor = "yellow", 
    highEndColor="red",
    sizeSummaryFunction = "sum",
    sizevar = "sample_size"
    ) %>% 
  addHexbin(
    data = temp_df,
    radius = 19, 
    lowEndColor = "white", 
    highEndColor="red",
    sizeSummaryFunction = "mean",
    sizevar = "temp"
    ) %>% 
  addHexbin(
    data = both_df,
    radius = 18, 
    lowEndColor = "white", 
    highEndColor="darkgreen",
    sizeSummaryFunction = "sum",
    sizevar = "sample_size",
    colorSummaryFunction = "median",
    colorvar = "temp"
    )
```


